\subsection{Excercise Answers}
\begin{question}
    \textbf{E 4} Construct a one-to-one correspondence between the closed unit interval
    \[
    [0, 1] = \{x \in \mathbb{R} \mid 0 \leq x \leq 1\}
    \]
    and the open unit interval \((0, 1)\).  

\end{question}
\begin{proof}
    To construct a one-to-one correspondence between the closed unit interval \([0, 1]\) and the open unit interval \((0, 1)\), we proceed as follows:

    1. We first define a bijection between the sequences \(\{0, 1, 1/2, 1/3, 1/4, \ldots\}\) and \(\{1/2, 1/3, 1/4, \ldots\}\). Let \(f\) be defined as:
    \[
    f(x) = 
    \begin{cases} 
    1/2 & \text{if } x = 0, \\
    1/3 & \text{if } x = 1, \\
    \frac{1}{n + 2} & \text{if } x = \frac{1}{n} \text{ for } n \geq 2.
    \end{cases}
    \]
    The inverse function \(f^{-1}\) is given by:
    \[
    f^{-1}\left(\frac{1}{x}\right) = 
    \begin{cases} 
    0 & \text{if } x = 2, \\
    1 & \text{if } x = 3, \\
    \frac{1}{x - 2} & \text{if } x > 3.
    \end{cases}
    \]

    2. For the remaining points in \([0, 1]\) that are not in the sequence \(\{0, 1, 1/2, 1/3, 1/4, \ldots\}\), we define a function \(g\) by:
    \[
    g(x) = 
    \begin{cases} 
    f(x) & \text{if } x \text{ is in the sequence}, \\
    x & \text{otherwise (identity map)}.
    \end{cases}
    \]
    This function \(g\) forms a bijection between \([0, 1]\) and \((0, 1)\).

\end{proof}
\begin{question}
    \textbf{E 6} Let $\kappa$ be a nonzero cardinal number. Show that there does not exist a set to which every set of cardinality $\kappa$ belongs.
\end{question}
\begin{proof}
    Proof by contradiction (BWOC): Assume that such a set exists. Let 
    \[ 
    A = \{ K \mid |K| = \kappa \} 
    \]
    be the set containing all sets with cardinality $\kappa$.

    Consider 
    \[
    \bigcup A,
    \]
    the union of all sets in $A$. By construction, $\bigcup A$ would be a set that contains every possible set of cardinality $\kappa$.

    However, this leads to a contradiction since such a set does not exist in the framework of standard set theory (e.g., due to limitations implied by Russell's paradox or cardinality constraints).

    Therefore, there does not exist a set $A$ such that it contains every set of cardinality $\kappa$.
\end{proof}

\begin{question}
    \textbf{E 7}
    Assume that $A$ is finite and $f: A \rightarrow A$. Show that $f$ is one-to-one if and only if $\text{ran } f = A$.
\end{question}
Given that $\text{ran } f = A$, this implies that $f$ is surjective.
Thus, the statement is equivalent to proving that: \textit{``Assume that $A$ is finite and $f: A \rightarrow A$. Show that $f$ is one-to-one if and only if $f$ is surjective.''}
\begin{proof}
Assume $A$ \text{ is finite.}
    \begin{itemize}
        \item (\(\Rightarrow\)) \textbf{(By way of contradiction):} Assume that $f$ is injective but not surjective. Then, the image of $f$ under $A$, denoted by $f[A]$, is a proper subset of $A$, meaning $f[A] \subsetneq A$. Thus, we have an injective function $f: A \rightarrow f[A]$. By construction, $f[A] = f[A]$, and therefore, $f$ is surjective onto $f[A]$. Hence, $f$ is a bijection from $A$ to $f[A]$, where $f[A] \subsetneq A$. According to Corollary 6D, this implies that $A$ is equinumerous to a proper subset of itself, which contradicts the assumption that $A$ is finite.

        \item (\(\Leftarrow\)) \textbf{(By way of contradiction):} Assume that $f$ is surjective but not injective. By the axiom of choice, there exists an injection, call it $g$, from $A$ to the preimage of $A$ under $f$, which is a proper subset of $A$. Such a function $g$ would then be a bijection from the preimage of $A$ to $A$. This again implies that $A$ is equinumerous to a proper subset of itself, leading to the conclusion that $A$ is infinite. This contradicts our original assumption that $A$ is finite.
    \end{itemize}
\end{proof}
\begin{question}
    \textbf{E 8}
    Prove that the union of two finite sets is finite (Corollary 6K), without any use of arithmetic.
\end{question}
\begin{proof}
    Let \(|A| \approx n\) and \(|B| \approx m\), where \(n, m \in \omega\). Assume that \(A\) and \(B\) are disjoint. By the definition of equinumerosity, there exist functions \(h: A \rightarrow n\) and \(g: B \rightarrow m\). We define a function \(f: A \cup B \rightarrow n + m\) (as defined earlier) such that

    \[
    f(x) = 
    \begin{cases} 
    h(x) & \text{if } x \in A \\
    n + g(x) & \text{if } x \in B
    \end{cases}
    \]

    This function is well-defined since \(A\) and \(B\) are disjoint. It is straightforward to verify that such an \(f\) is a bijection with an inverse \(f^{-1}: n + m \rightarrow A \cup B\) defined as follows:

    \[
    f^{-1}(k) = 
    \begin{cases} 
    h^{-1}(k) & \text{if } k \leq n \\
    g^{-1}(k - n) & \text{if } k > n
    \end{cases}
    \]

    If \(A\) and \(B\) are not disjoint, then let \(A \cap B = C \neq \emptyset\). Replace each element in \(C\) by elements not present in \(A \cup B\) to form a new set \(C'\). Let \(A' = (A - C) \cup C'\). We have \(|A'| = |A|\) and \(A \cup B \subseteq A' \cup B\), which forms a disjoint union. By Lemma 6F, there exists a \(k < n + m\) such that \(|A \cup B| = k\).

    Therefore, in both cases, \(A \cup B\) is finite.
\end{proof}
\begin{question}
    \textbf{E 9}
    Prove that the Cartesian product of two finite sets is finite (Corollary 6K), without any use of arithmetic.
\end{question}
\begin{proof}
    We will use induction to prove this statement:

    Let 
    \[
    S = \{ m \mid \forall n \in \omega, \forall A, B \text{ such that } |A| = m, |B| = n, |A \times B| = m \times n \},
    \]
    where \(\times\) is defined as the Cartesian product for natural numbers.

    \begin{enumerate}
        \item \textbf{Base Case:} \(0 \in S\). For any set \(B\), \(\emptyset \times B = \emptyset\). Thus, \(|\emptyset \times B| = 0 \times |B| = 0\) since \(B\) is finite and therefore \(|B| \in \omega\). Furthermore, \(1 \in S\) since for any singleton \(\{a\}\) and any set \(B\), there exists a bijection between \(\{a\} \times B\) and \(B\) given by the function \(f: \{a\} \times B \rightarrow B\) defined as \(f(a, x) = x\). The inverse function is \(g(x) = (a, x)\). Therefore, \(|\{a\} \times B| = 1 \times |B| = |B|\).
        
        \item \textbf{Inductive Step:} Assume \(k \in S\). We want to show that \(k^+ \in S\), where \(k^+\) denotes the successor of \(k\).
        
        To show \(k^+ \in S\), we need to prove that for all \(m \in \omega\) and for all sets \(A\) and \(B\) such that \(|A| = k^+\) and \(|B| = m\), we have \(|A \times B| = k^+ \times m\).
        
        Since we have already proven that \(0 \in S\), the induction starts with \(k \geq 1\), meaning \(k^+ \geq 2\).
        
        Let \(A\) be a set with \(|A| = k^+\). Since \(k^+ \geq 2\), there exists an element \(a \in A\). Let \(A' = A \setminus \{a\}\). Therefore, \(|A'| = k\), and by the induction hypothesis, \(|A' \times B| = k \times m\). Since \(\{a\}\) is a singleton, we have \(|\{a\} \times B| = 1 \times m = m\) by the induction hypothesis.
        
        Therefore,
        \[
        |A \times B| = |(A' \times B) \cup (\{a\} \times B)| = k \times m + m = k^+ \times m
        \]
        by the definition of multiplication for natural numbers.
    \end{enumerate}

    Hence, by induction, the Cartesian product of two finite sets is finite (since natural number is closed under multiplication).
\end{proof}
\begin{question}
    \textbf{E 10 to 12}
    For Excercises 10 to 12, proving all the Theorem 6I is suffices.
\end{question}
In Page 142
\begin{leftbar}
    \textbf{Theorem 6I} For any cardinal numbers \(\kappa\), \(\lambda\), and \(\mu\):

    \begin{enumerate}
        \item \(\kappa + \lambda = \lambda + \kappa\) and \(\kappa \cdot \lambda = \lambda \cdot \kappa\).
        \item \(\kappa + (\lambda + \mu) = (\kappa + \lambda) + \mu\) and \(\kappa \cdot (\lambda \cdot \mu) = (\kappa \cdot \lambda) \cdot \mu\).
        \item \(\kappa \cdot (\lambda + \mu) = \kappa \cdot \lambda + \kappa \cdot \mu\).
        \item \(\kappa^{\lambda + \mu} = \kappa^\lambda \cdot \kappa^\mu\).
        \item \((\kappa \cdot \lambda)^\mu = \kappa^\mu \cdot \lambda^\mu\).
        \item \((\kappa^\lambda)^\mu = \kappa^{\lambda \cdot \mu}\).
    \end{enumerate}

    \textbf{Proof} Take sets \(K\), \(L\), and \(M\) with \(\text{card } K = \kappa\), \(\text{card } L = \lambda\), and \(\text{card } M = \mu\); for convenience, choose them in such a way that any two are disjoint. Then each of the equations reduces to a corresponding statement about equinumerous sets. For example, \(\kappa \cdot \lambda = \text{card } (K \times L)\) and \(\lambda \cdot \kappa = \text{card } (L \times K)\); consequently, showing that \(\kappa \cdot \lambda = \lambda \cdot \kappa\) reduces to showing that \(K \times L \approx L \times K\). Listed in full, the statements to be verified are:

    \begin{enumerate}
        \item \(K \cup L \approx L \cup K\) and \(K \times L \approx L \times K\).
        \item \(K \cup (L \cup M) \approx (K \cup L) \cup M\) and \(K \times (L \times M) \approx (K \times L) \times M\).
        \item \(K \times (L \cup M) \approx (K \times L) \cup (K \times M)\).
        \item \({}^{(L \cup M)} K \approx {}^K L \times {}^k M\).
        \item \({}^M (K \times L) \approx {}^M K \times {}^M L\).
        \item \({}^{M} ({}^L K) \approx {}^{(L \times M)} K\).
    \end{enumerate}
\end{leftbar}
I will use the second part of 1 to 6 (on the set) to prove the theorem.
\begin{proof} For the simple ones I will simple list the fucntion without justifying that it is bijection.
    \begin{enumerate}
        \item \(K \cup L = L \cup K\) by algebra of set (Page 27). f: \(K \times L \rightarrow L \times K\) s.t. \(<k, l> \mapsto <l, k>\)
        \item \(K \cup (L \cup M) = (K \cup L) \cup M\) by algebra of set (Page 27). f: \(K \times (L \times M) \rightarrow (K \times L) \times M\) s.t. \(<k, <l, m>> \mapsto <<k, l>, m>\).
        \item \(K \times (L \cup M) = (K \times L) \cup (K \times M)\) by Excercise 2 Chapter3.
        \item \(H: {}^{(L \cup M)} K \rightarrow {}^K L \times {}^k M\) \(s.t. f \mapsto <f \upharpoonright {}_L, f \upharpoonright {}_{M - L}>\).
        \item \(H: {}^M (K \times L) \rightarrow {}^M K \times {}^M L\). Let \(f \in {}^M (K \times L) \), then \(\forall m \in M f: m \mapsto f(m) = <k, l> = <f_1(m), f_2(m)>\). Thus let \(H: f \mapsto <f_1, f_2>\).
        \item Proven in book. 
    \end{enumerate}
\end{proof}

\begin{question}
    \textbf{E 13}
    Show that a finite union of finite sets is finite. That is, show that if \(B\) is a finite set whose members are themselves finite sets, then \(\bigcup B\) is finite.
\end{question}
\begin{proof}
    In Chapter 6 E 3, we have proved that two finite set's union is finite. Do induction on natural number, we can prove that any finite union of finite sets is finite.
\end{proof}
\begin{question}
    \textbf{14}
    Define a \textit{permutation} of \(K\) to be any one-to-one function from \(K\) onto \(K\). We can then define the factorial operation on cardinal numbers by the equation
    \[
    \kappa! = \text{card} \{ f \mid f \text{ is a permutation of } K \},
    \]
    where \(K\) is any set of cardinality \(\kappa\). Show that \(\kappa!\) is well defined, i.e., the value of \(\kappa!\) is independent of just which set \(K\) is chosen.

\end{question}
\begin{proof}
    To show that \(\kappa!\) is well-defined, let \(\kappa\) be a cardinal number, and consider any two sets \(A\) and \(B\) such that \(|A| = |B| = \kappa\).

    Since \(A \approx A\), let \(f_A\) be a bijection \(f_A: A \rightarrow A\). Similarly, let \(f_B\) be a bijection \(f_B: B \rightarrow B\). Since \(A \approx B\), there exists a bijection \(f: A \rightarrow B\).

    We can establish a bijection between the set of permutations of \(A\) (denoted by \(\mathrm{perm}(A)\) or \(\mathrm{sym}(A)\)) and the set of permutations of \(B\) (denoted by \(\mathrm{perm}(B)\) or \(\mathrm{sym}(B)\)). This bijection can be constructed as follows: for any \(f_A \in \mathrm{perm}(A)\), we define a corresponding permutation of \(B\) by \(f_A' = f \circ f_B \circ f^{-1}\) (this is a conjugation by \(f\)).

    This construction is clearly a bijection between \(\mathrm{perm}(A)\) and \(\mathrm{perm}(B)\). Thus, the value of \(\kappa!\) is independent of the particular choice of the set \(K\) with cardinality \(\kappa\), proving that the factorial operation on cardinal numbers is well-defined.
\end{proof}
\begin{question}
    \textbf{E 15}
    Show that there is no set \(\mathcal{A}\) with the property that for every set there is some member of \(\mathcal{A}\) that dominates it.
\end{question}
\begin{proof}
    To prove that there is no such set \(\mathcal{A}\) with the stated property, we proceed by contradiction.

    \textbf{By way of contradiction (BWOC):} Assume that such a set \(\mathcal{A}\) exists. Let \(\mathcal{A}' = \bigcup \mathcal{A}\). By the definition of \(\mathcal{A}\), there exists a set \(K \in \mathcal{A}\) such that \(K\) dominates \(\mathcal{A}'\). Therefore, there is an injection from \(\mathcal{A}'\) to \(K\).

    By the definition of \(\mathcal{A}\), the power set \(2^K\) (the set of all subsets of \(K\)) is dominated by some element \(K' \in \mathcal{A}\). This means that there exists an injection from \(2^K\) to \(K'\). Since \(K' \in \mathcal{A}\) and \(\mathcal{A}' = \bigcup \mathcal{A}\), we have \(K' \subseteq \mathcal{A}'\). Therefore, the embedding of \(K'\) into \(\mathcal{A}'\) is a natural injection.

    Furthermore, we know that \(\mathcal{A}'\) injects into \(K\), and \(K\) injects into \(2^K\), since the power set of any set strictly dominates the set itself. Thus, we have an injection from \(2^K\) into \(\mathcal{A}'\). By the transitivity of injections (i.e., the property that injections are preserved under composition), this implies that \(2^K\) injects into \(K\), which contradicts the fact that the power set of a set always strictly dominates the set itself.

    Therefore, our initial assumption that such a set \(\mathcal{A}\) exists must be false.
\end{proof}

\begin{question}
    \textbf{E 16}
    Show that for any set \(S\) we have \(S \subseteq 2^S\), but \(S \not\approx 2^S\).
\end{question}
\begin{proof}
    To prove that for any set \(S\) we have \(S \subseteq 2^S\) but \(S \not\approx 2^S\), we proceed as follows:

    \textbf{1. Injection from \(S\) into \(2^S\):}  
    Define a function \(H: S \rightarrow {}^S 2\) such that \(H(x) \mapsto f_x\), where \(f_x: S \rightarrow \{0, 1\}\) is defined by:
    \[
    f_x(y) = 
    \begin{cases} 
    1 & \text{if } y = x \\
    0 & \text{otherwise}
    \end{cases}
    \]
    This function \(H\) is injective since distinct elements \(x, x' \in S\) will be mapped to distinct functions \(f_x\) and \(f_{x'}\).

    \textbf{2. Proving \(S \not\approx 2^S\):}  
    To show that \(S\) is not equinumerous to \(2^S\), we use a diagonal argument. Consider the function \(g: S \rightarrow \{0, 1\}\) defined by:
    \[
    g(x) = 1 - H(x)(x)
    \]
    We claim that the set \(B = \{g: g(x) = 1 - H(x)(x)\}\) is a subset of \({}^S 2\) but is not in the range of \(H\).

    \begin{proof} We prove by two parts: \\
        \(B \subseteq {}^S 2\): This is straightforward to show. Since \(H(x)(x) \in \{0, 1\}\), we have \(g(x) \in \{0, 1\}\) for all \(x \in S\). Therefore, \(g\) is a valid function from \(S\) to \(\{0, 1\}\), implying \(B \subseteq {}^S 2\). \\
        \(B\) is not in the range of \(H\): Suppose, for the sake of contradiction (BWOC), that there exists \(x \in S\) such that \(H(x) = g\). Then we have:
        \[
        H(x)(x) = 1 - H(x)(x)
        \]
        This implies:
        \[
        H(x)(x) = \frac{1}{2}
        \]
        which is a contradiction, since \(H(x)(x) \in \{0, 1\}\).

        Thus, we have shown that \(S \subseteq 2^S\) but \(S \not\approx 2^S\).
    \end{proof}

\end{proof}
\begin{question}
    \textbf{E 17}
    Give counterexamples to show that we cannot strengthen Theorem 6L by replacing "\(\leq\)" by "\(<\)" throughout.
\end{question}
Theorem 6L in Page 149:
\begin{leftbar}
    \textbf{Theorem 6L} Let \(\kappa\), \(\lambda\), and \(\mu\) be cardinal numbers.

    \begin{enumerate}
        \item[(a)] \(\kappa \leq \lambda \implies \kappa + \mu \leq \lambda + \mu\).
        \item[(b)] \(\kappa \leq \lambda \implies \kappa \cdot \mu \leq \lambda \cdot \mu\).
        \item[(c)] \(\kappa \leq \lambda \implies \kappa^\mu \leq \lambda^\mu\).
        \item[(d)] \(\kappa \leq \lambda \implies \mu^\kappa \leq \mu^\lambda\); if not both \(\kappa\) and \(\mu\) equal zero.
    \end{enumerate}
\end{leftbar}
\begin{proof}
    \textbf{A Concrete Example:}

    Consider the sets \(A = \{0, 1\}\) and \(B = \{0, 1, 2\}\).  
    We have \(|A| < |B|\), yet \(A \cup \omega \approx B \cup \omega\), which implies \(|A| + \aleph_0 = |B| + \aleph_0\).  
    The same holds for the other operations as well.

    \textbf{A More General and Abstract Example:}

    For any \(n, m \in \omega\) with \(n < m\), we have:
    \[
    n + \aleph_0 = m + \aleph_0, \quad n \times \aleph_0 = m \times \aleph_0,
    \]
    and similarly for the other cases.

\end{proof}

\begin{question}
    \textbf{E 18} 
    Prove that the following statement is equivalent to the axiom of choice: For any set $\mathcal{A}$ whose members are nonempty sets, there is a function $f$ with domain $\mathcal{A}$ such that $f(X) \in X$ for all $X \in \mathcal{A}$.
\end{question}
\begin{proof}
    To prove that the axiom of choice is equivalent to the given statement, we proceed as follows:

    \textbf{Axiom of Choice:} The axiom of choice states that for any relation \( R \), there exists a function \( f \subset R \) such that \( \mathrm{dom} \, f = \mathrm{dom} \, R \).

    \textbf{To Show:}
    \[
    \text{Axiom of Choice} \iff \text{Given Statement}
    \]

    \textbf{(Forward Implication):} Assume the axiom of choice holds. Let 
    \[
    R := \{ \langle X, x \rangle \mid x \in X \in \mathcal{A} \}.
    \]
    By the axiom of choice, there exists a function \( f \subset R \) such that \( \mathrm{dom} \, f = \mathrm{dom} \, R = \mathcal{A} \). This function \( f \) satisfies the required condition: for all \( X \in \mathcal{A} \), \( f(X) \in X \).

    \textbf{(Reverse Implication):} Assume the given statement holds. Let \( R \) be a relation and \( K = \mathrm{dom} \, R \). Define
    \[
    \mathcal{A} = \{ X_{x_r} \subseteq K \mid x_r \in \mathrm{ran} R, \forall x \in X, xRr_x \text{ and } X \neq \emptyset \}.
    \]
    By the assumption, there exists a function \( f \) such that for all \( X \in \mathcal{A} \), \( f(X) \in X \). This function \( f \) has \( \mathrm{dom} \, f = \mathcal{A} = \mathrm{dom} \, R \).

\end{proof}

\begin{question}
    \textbf{E 19} 
    Assume that $H$ is a function with finite domain $I$ and that $H(i)$ is nonempty for each $i \in I$. Without using the axiom of choice, show that there is a function $f$ with domain $I$ such that $f(i) \in H(i)$ for each $i \in I$. \textit{[Suggestion: Use induction on $\text{card } I$.]}
\end{question}

\begin{question}
    \textbf{E 20 } 
    Assume that \( A \) is a nonempty set and \( R \) is a relation such that 
    \[
    \forall x \in A, \exists y \in A \text{ such that } yRx.
    \]
    Show that there exists a function \( f: \omega \to A \) with 
    \[
    f(n^+) R f(n) \quad \text{for all } n \in \omega.
    \]
\end{question}
\begin{proof}
    Given that \( R \subset A \times A \) is a "surjective" relation on \( A \), we can define \( R' = R^{-1} := \{ \langle x, y \rangle \mid \langle y, x \rangle \in R \} \), which is also a relation on \( A \). By the axiom of choice, there exists a function \( g \subset R' \) such that \( \operatorname{dom} g = \operatorname{dom} R' = A\).

    Since \( A \) is nonempty, it contains at least one element. Let \( x \in A \) be such an element. We can define a function \( f: \omega \to A \) recursively as follows:

    \begin{enumerate}
        \item \( f(0) = x \).
        \item \( f(n^+) = g(f(n)) \), where \( g \) is the function induced by \( R' \).
    \end{enumerate}

    Since \( g \) is a function derived from the inverse relation \( R' \), it follows that \( f(n^+) \, R \, f(n) \) for all \( n \in \omega \).

    By a simple induction, we can also show that \( \operatorname{dom} f = \omega \), ensuring that \( f \) is defined on all natural numbers.
\end{proof}
\begin{question}
    \textbf{E 21}
    \textbf{Teichmüller--Tukey Lemma:} Assume that \(\mathcal{A}\) is a nonempty set such that for every set \(B\),
    \[
    B \in \mathcal{A} \iff \text{every finite subset of } B \text{ is a member of } \mathcal{A}.
    \]
    Show that \(\mathcal{A}\) has a maximal element, i.e., an element that is not a subset of any other element of \(\mathcal{A}\).
\end{question}
\textbf{Zorn's Lemma:}
Let \(\mathcal{A}\) be a set such that for every chain \(\mathcal{B} \subseteq \mathcal{A}\), we have \(\bigcup \mathcal{B} \in \mathcal{A}\). (\(\mathcal{B}\) is called a \textbf{chain} if for any \(C\) and \(D\) in \(\mathcal{B}\), either \(C \subseteq D\) or \(D \subseteq C\).) Then \(\mathcal{A}\) contains a maximal element \(M\) such that \(M\) is not a subset of any other set in \(\mathcal{A}\).

Our goal is to verify the conditions of Zorn's Lemma for the set \(\mathcal{A}\), and then conclude that \(\mathcal{A}\) contains a maximal element.

To apply Zorn's Lemma, we need to show that for every chain \(\mathcal{B} \subseteq \mathcal{A}\), the union \(\bigcup \mathcal{B}\) is in \(\mathcal{A}\). This means we need to prove:
\begin{enumerate}
    \item \(\mathcal{B}\) is a chain in \(\mathcal{A}\).
    \item \(\bigcup \mathcal{B} \in \mathcal{A}\).
\end{enumerate}

Since \(\mathcal{B}\) is any chain in \(\mathcal{A}\), we focus on proving that \(\bigcup \mathcal{B} \in \mathcal{A}\).

According to the defining property of \(\mathcal{A}\):

\[
B \in \mathcal{A} \iff \text{every finite subset of } B \text{ is in } \mathcal{A}.
\]

So, to show that \(\bigcup \mathcal{B} \in \mathcal{A}\), we need to demonstrate that \textbf{every finite subset of \(\bigcup \mathcal{B}\) is in \(\mathcal{A}\)}.
\begin{proof}
    Let \(\mathcal{B}\) be a chain s.t. \(\mathcal{B} \subseteq \mathcal{A}\). Let \(F\) be any finite subset of \(\bigcup \mathcal{B}\). For each element \(x \in F\), there exists a set \(B_x \in \mathcal{B}\) such that \(x \in B_x\). This is because \(x\) is in \(\bigcup \mathcal{B}\), so it must belong to at least one member of \(\mathcal{B}\).
    
    Since \(\mathcal{B}\) is a chain, the sets \(B_x\) are comparable by inclusion. For any two elements \(x, y \in F\), either \(B_x \subseteq B_y\) or \(B_y \subseteq B_x\). Because \(F\) is finite, the collection \(\{B_x : x \in F\}\) is finite. We can find a maximal set \(B_0\) among \(\{B_x : x \in F\}\) with respect to inclusion. 
    
    Since \(B_0 \in \mathcal{A}\), and \(F \subseteq B_0\), we can conclude that \(F \in \mathcal{A}\). Thus \(\bigcup \mathcal{B} \in \mathcal{A} \), which satisfies conditions for zorn's lemma.
\end{proof}

\begin{question}
    \textbf{E 22} 
    Show that the following statement is another equivalent version of the axiom of choice: For any set \(A\) there is a function \(F\) with \(\operatorname{dom} F = \bigcup A\) and such that \(x \in F(x) \in A\) for all \(x \in \bigcup A\).
\end{question}
\begin{proof}
    To show: \textbf{Axiom of Choice (AC)} \(\iff\) statement.

    \((\Rightarrow)\) Assume \(A\) is a set. Consider the relation \(R = \{ \langle x, X \rangle \mid X \in A, x \in X \}\). By the Axiom of Choice, there exists a function \(f \subseteq R\) such that \(\operatorname{dom} f = \operatorname{dom} R\). Clearly, \(\operatorname{dom} R = A\). Additionally, for all \(x \in \bigcup A\), we have \(x \in f(x) \in A\). Thus, we have found such a function \(f\).

    \((\Leftarrow)\) Let \(R\) be a relation. Let \(K = \operatorname{dom} R\). Define
    \[
    A = \{X_r \subseteq K \mid x_r \in \operatorname{ran} R, \forall x \in X_r, x R x_r\}.
    \]
    By assumption, there exists a function \(f\) with \(\operatorname{dom} f = \bigcup A = \operatorname{dom} R\).

\end{proof}

\begin{question}
    \textbf{E 26} 
    Prove the following generalization of Theorem 6Q: If every member of a set \(\mathcal{A}\) has cardinality \(\kappa\) or less, then
    \[
    \mathrm{card} \bigcup \mathcal{A} \leq (\mathrm{card} \, \mathcal{A}) \cdot \kappa.
    \]
\end{question}

\begin{question}
    \textbf{E 27} 
    \begin{enumerate}
        \item Let \( A \) be a collection of circular disks in the plane, no two of which intersect. Show that \( A \) is countable.
        \item Let \( B \) be a collection of circles in the plane, no two of which intersect. Need \( B \) be countable?
        \item Let \( C \) be a collection of figure eights in the plane, no two of which intersect. Need \( C \) be countable?
    \end{enumerate}
\end{question}
\begin{proof} Use Rational numbers.
    \begin{enumerate}
        \item Every disck include at least one rational number. If it is countable, then there must be two circle containing same rational number, contardiction to pair wise disjoint.
        \item No. Consider \(B = \{B_r(0) | r \in (0, 1]\}\)
        \item Yes. Pick one eight shape in the conllections. Three conditions for second eight, either in one of the circle of first eight or outside of the first eight: if all the eight is pair wise outside, then it is the same as eight shaped disk, appying the first arguement it is countable. If on the other hand in one of the circles, then the second disk's diameter (greatest length) is decreased by 2 wetice at least. This will form a sequence for eight shapes that is countable (since there is at least one rational number that is between two shapes.). Or in another way we can argue that there must be a rational number included in the difference of two eight, thus must be countable since difference shape is more than eight shape.
    \end{enumerate}
\end{proof}